---
title: "Experimental OmicsDS interface in R"
description: "This document describes the interface to the OmicsDS C++ library in R and reviews the patterns and conventions of the R package."
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{omicds}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(omicsds)
print(omicsds::version())
```

This is work in progress. The `OmicsDS` C++ library allows for ingestion and export of feature-level matrix, interval-level and SAM Omics data into its data store. The `omicsds` package provides an R query interface into this C++ library.

# Features


## Ingestion

Currently, ingestion is supported for feature-level matrices(e.g. single cell matrices serialized from Seurat objects), interval-level bed data and SAM files into `OmicsDS`, only from the `CLI`. Input data can be ingested/persisted from/to cloud storage(s3, gcs and azure) or posix filesystems.

## Export

Export is supported from the R interface in the form of queries to get R DataFrame slices of data stored in `OmicsDS`.
